PANCHANGE_analysis

### 2020-08-20 PANCHANGE_analysis.Rmd

```{r}
dat %>%
  filter(is.na(Disorder)) %>%
  freq(Sample)
```

@@

```{r Disorder_inc by Gender}
Disorder_by_Gender <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder_inc, Gender) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

```{r Disorder_inc by Gender}
Disorder_inc_by_Gender <- dat.long.psych %>%
  group_by(Disorder_inc) %>%
  filter(Diagnosis == 1) %>%
  count(Gender) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

@@

@@

### Summary scores
```{r descriptives gad.diff_score_cols}
gad.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = gad.sum_score_prepan,
      "Base" = gad.sum_score_base,
      "Retro" = gad.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r gad gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

@@

### Summary scores
```{r descriptives phq.diff_score_cols}
phq.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = phq.sum_score_prepan,
      "Base" = phq.sum_score_base,
      "Retro" = phq.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

### Summary scores
```{r descriptives ocir.diff_score_cols}
ocir.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = ocir.sum_score_prepan,
      "Base" = ocir.sum_score_base,
      "Retro" = ocir.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

Model 0: Disorders
```{r}
model0 <- lm(
  formula = gad.diff_score_prepan_retro ~ Disorder,
  data = dat)

@@

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = gad.diff_score_base_retro ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
  data = dat)

@@

```{r descriptives pcl.diff_score_cols}
pcl.sum_score_numeric_table <- dat %>% 
#    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = pcl.sum_score_prepan,
      "Base" = pcl.sum_score_base
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

>>>>

Investigate NAs 
Ask Leo?
```{r NAs in diagnosis}
dat %>%
  filter(is.na(Disorder)) %>%
  freq(Sample)
```

@@

```{r Disorder_inc by Gender}
Disorder_inc_by_Gender <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder_inc, Gender) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

```{r Disorder_inc by Gender prop}
Disorder_inc_by_Gender <- dat.long.psych %>%
  group_by(Disorder_inc) %>%
  filter(Diagnosis == 1) %>%
  count(Gender) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

100% bar per diagnosis with percentages of contribution per sample

@@

+++CHECK OVERLAP BETWEEN TESTS and probable COVID

@@

### Summary scores
```{r descriptives gad.sum_score_cols}
gad.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = gad.sum_score_prepan,
      "Base" = gad.sum_score_base,
      "Retro" = gad.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r gad gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r gad percentage plot prepan_retro}
dat.long.gad.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

@@

### Summary scores
```{r descriptives phq.sum_score}
phq.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = phq.sum_score_prepan,
      "Base" = phq.sum_score_base,
      "Retro" = phq.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

### Summary scores
```{r descriptives ocir.sum_score}
ocir.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = ocir.sum_score_prepan,
      "Base" = ocir.sum_score_base,
      "Retro" = ocir.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

Model 0: Disorders
```{r}
model0 <- lm(
  formula = phq.diff_score_base_prepan ~ Disorder,
  data = dat)

Model 0: Disorders
```{r}
model0 <- lm(
  formula = gad.diff_score_base_prepan ~ Disorder,
  data = dat)

@@

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = phq.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
  data = dat)

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = gad.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
  data = dat)

@@

```{r descriptives pcl.sum_score}
pcl.sum_score_numeric_table <- dat %>% 
#    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = pcl.sum_score_prepan,
      "Base" = pcl.sum_score_base
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )
